Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/related-work.tex
[ paper ] fixed related work.

\citeauthor{Kanso2012} in~\cite{Kanso2012,kanso2016light} presents a proof-
reconstruction in \Agda for propositional logic. Its tool support proof-
reconstruction for \name{EProver} and \name{Z3} ATPs following a similar work-
flow as we presented in Section~\ref{ssec:workflow}. Nonetheless, his approach
employs semantics for logic equivalences. We have avoided the use of
propositions meanings towards a future work to support other logics where a
syntactical approach plays an important role~(for an example of such logics, we
refer the reader to \cite{Agudelo-Agudelo2017}).
\citeauthor{foster2011integrating}~\cite{foster2011integrating} describe  the
proof-reconstruction in \Agda for \name{Waldmeister}~\cite{hillenbrand1997}, a
prover for pure equational logic. As far as we know, no other proof-
reconstruction has been carried out in \Agda and with \Metis prover.

>>>>

\citeauthor{Kanso2012} in~\cite{Kanso2012,kanso2016light} presents a
proof-reconstruction in \Agda for propositional logic. Its tool support
proof-reconstruction for \name{EProver} and \name{Z3} ATPs following a similar work-flow as we presented in Section~\ref{ssec:workflow}.
Nonetheless, its approach
employs semantics for logic equivalences. We have avoided the use of
propositions meanings towards a future work to support other logics where a
syntactical approach plays an important role~(for an example of such logics, we
refer the reader to \cite{Agudelo-Agudelo2017}).
\citeauthor{foster2011integrating}~\cite{foster2011integrating} describe  the
proof-reconstruction in \Agda for \name{Waldmeister}~\cite{hillenbrand1997}, a
prover for pure equational logic. As far as we know, no other proof-
reconstruction has been carried out in \Agda and with \Metis prover.
